Identification of protoneutron star g-modes in gravitational-wave data

### 2020-08-06 methods.tex
Method section update
Table with estimates

\begin{equation}
r_i=\beta_1 f_i + \beta_2 f_i^2 +\beta_3 f_i^3 + \epsilon_i
\end{equation}
where $\epsilon_i$ are assumed to be independent zero-mean Gaussian errors with
variances $\sigma_i^2$ that increase with frequency $f_i$. The model for frequency-dependent
variances is
\begin{equation}
\log \sigma_i=\alpha_0+ \alpha_1 f_i + \alpha_2 f_i^2 + \delta_i
\end{equation}
with independent and identically zero-mean Gaussian errors $\delta_i$. The R-package LMVAR
\cite{lmvar:2019} that implements a maximum likelihood approach was used to fit the model.
The best fitting model amongst polynomials of degree 1, 2, and 3  was chosen according to
the Aikaike information criterion with coefficients given in Table \ref{tab:model},

\begin{equation}\label{eq:universal}
r_i = \beta_1 f_i + \beta_3 f_i^3 + \epsilon_i
\end{equation}

The best-fitting model achieves a coefficient of determination of $R^2=0.9812$.
The data and fit of the model including 95\% confidence bands are displayed in
Figure \ref{fig:LMVAR}.

\begin{table}[h]
  \begin{tabular}{lll}
    \hline
    Coefficient & Estimate & standard error \\
    \hline
    $\beta_1$   & $6.09 \times 10^{-7}$ & $1.75 \times 10^{-8}$ \\
    $\beta_3$   & $6.24 \times 10^{-13}$ & $8.79 \times 10^{-15}$ \\
    \hline
  \end{tabular}
\caption{Estimate and standard error of the coefficients of the best fit model describing the ratio $r=M_{\rm PNS}/R_{\rm PNS}^2$ as function of the frequency of the $\mbox{}^2g_2$ mode.}\label{tab:model}
\end{table}

>>>>

\begin{equation}
\label{model1}
r_i=\beta_1 f_i + \beta_2 f_i^2 +\beta_3 f_i^3 + \epsilon_i
\end{equation}
where $\epsilon_i$ are assumed to be independent zero-mean Gaussian errors with
variances $\sigma_i^2$ that increase with frequency $f_i$. The model for frequency-dependent
variances is
\begin{equation}
\log \sigma_i=\alpha_0+ \alpha_1 f_i + \alpha_2 f_i^2 + \delta_i
\end{equation}
with independent and identically zero-mean Gaussian errors $\delta_i$. The R-package \texttt{lmvar}
\cite{lmvar:2019} that implements a maximum likelihood approach was used to fit the model.

The best fitting model amongst polynomials of degree 1, 2, and 3  was chosen according to
the Aikaike information criterion with coefficients given in Table \ref{tab:model}, which is actually the model defined in \eqref{model1}.  The data and fit of the model including 95\% confidence bands are displayed in
Figure~\ref{fig:LMVAR}.

%\begin{equation}\label{eq:universal}
%r_i = \beta_1 f_i + \beta_3 f_i^3 + \epsilon_i
%\end{equation}

%The best-fitting model achieves a coefficient of determination of $R^2=0.9812$.
%The data and fit of the model including 95\% confidence bands are displayed in
%Figure~\ref{fig:LMVAR}.

\begin{table}[h]
%  \begin{tabular}{lll}
%    \hline
%    Coefficient & Estimate & standard error \\
%    \hline
%    $\beta_1$   & $6.09 \times 10^{-7}$ & $1.75 \times 10^{-8}$ \\
%    $\beta_3$   & $6.24 \times 10^{-13}$ & $8.79 \times 10^{-15}$ \\
%    \hline
%  \end{tabular}

  \begin{tabular}{crr}
    \hline
    Coefficient & \multicolumn{1}{c}{Estimate} & Standard error \\
    \hline
   $\beta_1$  &  $ 1.00 \times 10^{-06}$ & $2.12 \times 10^{-08}$ \\   
   $\beta_2$  &  $-8.22 \times 10^{-10}$ & $5.00 \times 10^{-11}$ \\
   $\beta_3$  &  $ 1.01 \times 10^{-12}$ & $2.70 \times 10^{-14}$ \\
   $\alpha_0$ &  $-1.02 \times 10^{+01}$ & $6.80 \times 10^{-02}$ \\
   $\alpha_1$ &  $ 7.24 \times 10^{-04}$ & $1.56 \times 10^{-04}$ \\
   $\alpha_2$ &  $ 6.23 \times 10^{-07}$ & $8.15 \times 10^{-08}$ \\   
    \hline
  \end{tabular}
\caption{Estimate and standard error of the coefficients of the best fit model describing the ratio $r=M_{\rm PNS}/R_{\rm PNS}^2$ as function of the frequency of the $\mbox{}^2g_2$ mode.}\label{tab:model}
\end{table}
